Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-16 paper/paper.tex
minor fixes

Table~\ref{tab:cross-testing} shows the number of failures for each
pair of test suite and engine. The first column shows the test suites
and the first row shows the engines that run those tests. We use a
dash (``-'') to indicate that we did not consider the combinations
that associated a test suite with its parent engine; failures in those
cases would either indicate regressions or flaky tests as opposed to
an unknown bug for that engine. We did not run the test cases that
fail on its parent engine in any other engines; we wanted all tests to
pass on their parent engine as a failure in that case would be a
stronger indicative of a bug. In total, 64 test cases were discarded
for that reason--6 from \jsc{} and 58 from \smonkey. In total, 7,029
test files (\ie{}, 38369-31276-64) were considered in this experiment,
which involved 24,922 test runs (\ie, (7029*4)-1021-57-2116).  Of
these, 812 failures were observed (3.25\% of the runs) across
\textbf{543} distinct files (7.72\% of the files). We analyzed each of
these file in separate to identify if the failure was fault-revealing
or a false positive.

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 2 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 279 \\
    Duktape & 0 & 4 & 4 & 1   \\
    \jerry{} & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\
    Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 270 & 145 & 36 & 361 \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

\begin{table*}[t]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test transplantation.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
   2  & 4/23 & \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
   3  & 4/29 & \chakra{}  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}} & 2 & \smonkey{} \\
   \midrule
    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                       &  &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
   \midrule
   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
   6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
   7 & 5/21  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
   8 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
   9 & 7/10  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
   10 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
   12 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
   13 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
   14 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
   15 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
   16 & 8/08  & V8 & \textbf{Assigned} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
   17 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
   \bottomrule
  \end{tabular}
\end{table*}

>>>>

Table~\ref{tab:cross-testing} shows the number of failures for each
pair of test suite and engine. The first column shows the test suites
and the first row shows the engines that run those tests. We use a
dash (``-'') to indicate that we did not consider the combinations
that associated a test suite with its parent engine; failures in those
cases would either indicate regressions or flaky tests as opposed to
an unknown bug for that engine. We did not run the test cases that
fail on its parent engine in any other engines; we wanted all tests to
pass on their parent engine as a failure in that case would be a
stronger indicative of a bug. In total, 64 test cases were discarded
for that reason--6 from \jsc{} and 57 from \smonkey. In total, 7,029
test files (\ie{}, 38369-31276-64) were considered in this experiment,
which involved 24,922 test runs (\ie, (7029*4)-1021-57-2116).  Of
these, 812 failures were observed (3.25\% of the runs) across
\textbf{543} distinct files (7.72\% of the files). We analyzed each of
these file in separate to identify if the failure was fault-revealing
or a false positive.

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 2 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 217 & 106 & - & 278 \\
    Duktape & 0 & 4 & 4 & 1   \\
    \jerry{} & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\
    Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 270 & 145 & 36 & 361 \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

\begin{table*}[t]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test transplantation.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
   2  & 4/23 & \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
   3  & 4/29 & \chakra{}  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}} & 2 & \smonkey{} \\
   \midrule
    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                       &  &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
   \midrule
   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
   6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
   7 & 5/21  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
   8 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
   9 & 7/10  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
   10 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
   12 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5549}{\#5549}} & 2 & \jerry{}\\
   13 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
   14 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
   15 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
   16 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
   17 & 8/08  & V8 & \textbf{Fixed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
   18 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
   \bottomrule
  \end{tabular}
\end{table*}
